Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-29 papers/LREC2020/intro.tex
LREC2020: adds comments Sect.1-3

Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily results in linguistic variation.
For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.

@@

In this paper, we take a first step towards building a dataset with object naming data for real-world images. We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}. As a starting point, we compare three popular datasets in L\&V: \refcoco, a collection of referring expressions, \flickr, a collection of captions, and \vgenome, which features extensive region-level annotations. We observe that the object name annotations in these corpora suggest that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or analysis.

@@

The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomical relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.

>>>>

Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily \cs{necessarily??? \ra inherently? naturally?} results in linguistic variation.
For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.

@@

In this paper, we take a first step towards building a dataset with object naming data for real-world images. We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}. As a starting point, we compare three popular datasets in L\&V: \refcoco \cs{CITE}, a collection of referring expressions, \flickr \cs{CITE}, a collection of captions\cs{no, Flickr30K is a collection of captions, F Entities \ra of region-to-phrase linkings for image captions}, and \vgenome \cs{CITE -- at least VisualGenome should be cited}, which features extensive region-level annotations. We observe that the object name annotations in these corpora suggest that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or linguistic analysis.

@@

The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the basic-level \cs{explain basic-level, and if only with a reference or in a footnote} \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic (i.e.,\ hierarchical) relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.

### 2019-11-29 papers/LREC2020/lrec2020naming.tex
LREC2020: adds comments Sect.1-3

@@

\abstract{
People choose particular names for objects, such as \word{dog} or \word{puppy} for a given dog.
Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics (CL).
We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
Our dataset, ManyNames, provides 36 name annotations for each of 25K images selected from VisualGenome.
We highlight the challenges involved and provide a preliminary analysis of the ManyNames data that, on the one hand, shows high consistency in naming, and on the other, suggests that the main source of variation analyzed to date (taxonomic variation, as in \word{chihuahua} vs.\ \word{dog}) may not be the main driver of diversity in naming behavior, at least in our setup.
% , contrary to expectation, hierarchical variation is not the main source of 
% Massive data collections for applications in language \& vision are nowadays available. In principle, these could constitute valuable resources also for research in computational linguistics (CL). However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets. In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely naming of objects in real-world images. Our analysis of existing resources in language \& vision reveals that available datasets do not generally provide the right type and consistent quality of object naming data,  for being able to conduct a linguistically motivated study of this phenomenon. We contribute a new dataset on top of Visual Genome that  \sz{... continue}
 \\ \newline \Keywords{object naming, language and vision, computer vision} }

@@

\section{Introduction}
\input{intro}

>>>>

\usepackage{microtype}

@@

\abstract{
People choose particular names for objects, such as \word{dog} or \word{puppy} for a given dog.
Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics.
We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
Our dataset, ManyNames, provides 36 name annotations for each of 25K images\cs{objects} selected from VisualGenome.
We highlight the challenges involved and provide a preliminary analysis of the ManyNames data that, on the one hand, shows high consistency in naming, and on the other, suggests that the main source of variation analyzed to date (taxonomic variation, as in \word{chihuahua} vs.\ \word{dog}) may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
% , contrary to expectation, hierarchical variation is not the main source of 
% Massive data collections for applications in language \& vision are nowadays available. In principle, these could constitute valuable resources also for research in computational linguistics (CL). However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets. In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely naming of objects in real-world images. Our analysis of existing resources in language \& vision reveals that available datasets do not generally provide the right type and consistent quality of object naming data,  for being able to conduct a linguistically motivated study of this phenomenon. We contribute a new dataset on top of Visual Genome that  \sz{... continue}
 \\ \newline \Keywords{object naming, language and vision, computer vision} }

@@

\cs{maybe streamline use of (i),(ii),... and (1),(2),...}
\section{Introduction}
\input{intro}
